
\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage[margin=0.75in]{geometry}
\linespread{0.9}  
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\LARGE\bf Joseph F. Dyer} % Your name at the top
 
 
\moveleft.5\hoffset\centerline{joeydyer99@gmail.com} % Your address
\moveleft.5\hoffset\centerline{Vienna, VA 22180}
\moveleft.5\hoffset\centerline{(540)-687-0055}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{PROFILE}  

Full-Stack Developer with 4+ years of experience across front-end and back-end systems, focused on supporting Sponsors by evaluating emerging technologies and delivering innovative solutions to address their real-world challenges.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\sl Bachelors of Computer Science, Virginia Polytechnic Institute and State University}  
Honors: Summa Cum Laude, Phi Beta Kappa \hfill Sept, 2018 - May, 2021\\
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE} 


{\sl Intermediate Software Engineer, The MITRE Corporation} \hfill May, 2021-Present\\
\makebox[\textwidth][r]{Mclean, VA}

\begin{itemize} 
\item Led design and development of a 3 person team for an internal DevSecOps evaluation tool that informed a Sponsor’s contract award decision.
\item Built reusable web components to streamline front-end development and ensure compliance with federal design standards across a Sponsor’s organization.
\item Built full-stack MVP dashboards using Angular, AngularJS, Vue.js, Flask, and Express to demonstrate research capabilities and support Sponsor funding decisions.
\item Used Pentaho Data Integration, Python, and SQL stored procedures to automate data analytics reporting, reducing manual effort and saving time for Sponsors.

\end{itemize}
 
{\sl Teaching Assistant (DSA), Virginia Tech} \hfill Aug, 2020- May, 2021  \\
\makebox[\textwidth][r]{Blacksburg, VA}

\begin{itemize} 
\item Held office hours to explain complex algorithmic concepts and visually demonstrate advanced data structures to students. 
\item Assisted students in debugging and understanding challenging algorithm implementations through hands-on guidance.
\item Evaluated student projects, focusing on algorithmic correctness, efficiency, and conceptual understanding.
\end{itemize} 

{\sl Software Engineering Intern, The MITRE Corporation} \hfill Summers 2018-2020  \\
\makebox[\textwidth][r]{Mclean, VA}

\begin{itemize}
\item Delivered high-quality software enhancements that enabled sponsor collaboration on new user-facing capabilities, earning recognition for efficiency and effectiveness. (2020)
\item Independently delivered AWS-based ETL solutions and reusable tools that streamlined workflows and contributed technical insights to a whitepaper on Cloud vs. On-Premise vs. Hybrid analytics solutions. (2019)
\item Led a team of interns in stress testing an operational tool using Python to generate performance metrics for a sponsor deliverable. (2018)
\end{itemize} 

\section{Skills}
\textbf{Programming Languages:} JavaScript, Python, SQL, Java \\
\textbf{Frameworks:} Angular, AngularJS, Vue.js, Express, Flask \\
\textbf{Cloud \& AWS Tools:}  Currently Pursuing Associate AWS Solution Architect Certification, S3, Glue, SageMaker, Redshift, EC2, Lambda \\
\textbf{Databases:} PostgreSQL, Microsoft SQL Server, MySQL, Neo4j, MongoDB \\
\textbf{Tools \& Platforms:} Docker, Git, Kubernetes, Pentaho Data Integration
\end{resume}
\end{document}